Mastery Learning in Practice:\\ A Descriptive Analysis of Data from the Cognitive Tutor Algebra I Effectiveness Trial

### 2017-10-10 paper.Rnw
fixed bugs

\subsection{Where To?}
\begin{figure}
<<transition,fig.height=5,fig.width=6,dependson=c('data','setup')>>=
#### what's the next section each student works?
secOrder <- data%>%filter(is.finite(status) & is.finite(timestamp))%>%group_by(field_id,section,unit,Curriculum,overall,year,Year,Yr,state,classid2,schoolid2)%>%summarize(time=max(timestamp),status=max(status))%>%arrange(time)%>%group_by(field_id,year,Year,Yr,state,classid2,schoolid2)%>%mutate(prevSec=c(NA,section[-n()]),prevStatus=c(NA,status[-n()]),prevUnit=c(NA,unit[-n()]))

@@

transitionPlot(trans)

>>>>

\subsection{Where To?}
\begin{figure}
<<transition,fig.height=5,fig.width=6,dependson=c('data','setup')>>=
#### what's the next section each student works?
secOrder <- data%>%filter(is.finite(status) & is.finite(timestamp))%>%group_by(field_id,section,unit,Curriculum,overall,year,Year,Yr,state,classid2,schoolid2)%>%summarize(time=max(timestamp),status=max(status))%>%arrange(time)%>%group_by(field_id,year,Year,Yr,state,classid2,schoolid2)%>%mutate(prevSec=c(NA,section[-n()]),prevStatus=c(NA,status[-n()]),prevUnit=c(NA,unit[-n()]),nextUnit=c(unit[-1],NA))

secOrder$cp <- secOrder$status=='changed placement'
secOrder$mast <- secOrder$status=='graduated'

@@

#transitionPlot(trans)
